---
title: "ATAC RNA and combined ordering"
output: html_notebook
---

We first have to order cells in the combined data frame.
```{r}
#first order cells based on the cobined data frame

library(monocle)
library(Seurat)
library(stringr)
#make cds
#Load Seurat object of combedding
seurat_object<-readRDS("coembed_final_standard_norm_singlet_filt.rds")

cell<-str_split_fixed(seurat_object[["annot2"]][,1],"_",3)[,2]
cell<-gsub("Trametinib","Tram",cell)
cell<-gsub("HCCMDAMB468","MDA",cell)
cell<-gsub("SUM149PT","SUM",cell)
cellt<-str_split_fixed(cell,"_",2)[,1]
treatment<-str_split_fixed(cell,"_",2)[,2]
celltype<-seurat_object[["annot2"]]
celltype$cell<-cellt
celltype$treatment<-treatment
celltype$annot2<-NULL
seurat_object <- AddMetaData(seurat_object, metadata = celltype)



#Extract data, phenotype data, and feature data from the SeuratObject
data <- as(as.matrix(seurat_object@assays$RNA@data), 'sparseMatrix')

pd <- new('AnnotatedDataFrame', data = seurat_object@meta.data)

fData <- data.frame(gene_short_name = row.names(data), row.names = row.names(data))
fd <- new('AnnotatedDataFrame', data = fData)

#Construct monocle cds
monocle_cds <- newCellDataSet(data,
                              phenoData = pd,
                              featureData = fd,
                              lowerDetectionLimit = 0.5,
                              expressionFamily = negbinomial.size())

FM <- exprs(monocle_cds)
monocle_cds@auxOrderingData$normalize_expr_data <- FM

pca_res<- Embeddings(seurat_object, reduction= "pca")
#PCA
monocle_cds@normalized_data_projection <- as.matrix(t(pca_res))


cds_dims_data<- read.delim("COEMBED_res_CCA_results.UMAP.dims",header=F,row.names=1)



dim_no<-ncol(cds_dims_data)
S <- t(cds_dims_data)
Y <- S
W <- as.matrix(t(pca_res))
#(seurat_object$cca.aligned@cell.embeddings)
A <- S
colnames(A) <- colnames(monocle_cds)
colnames(S) <- colnames(monocle_cds)
colnames(Y) <- colnames(monocle_cds)
reducedDimA(monocle_cds) <- A
monocle_cds@reducedDimW<- W
monocle_cds@reducedDimS <- as.matrix(Y)
monocle_cds@reducedDimK <- S
monocle_cds@dim_reduce_type <- "UMAP"
pData(monocle_cds)$umap_1 = reducedDimA(monocle_cds)[1, ]
pData(monocle_cds)$umap_2 = reducedDimA(monocle_cds)[2, ]
if(dim_no==3){
  pData(monocle_cds)$umap_3 = reducedDimA(monocle_cds)[3, ]
}


saveRDS(monocle_cds,file="coembed_monocle3_format.rds")

cds<-readRDS("coembed_monocle3_format.rds")

cds <- detectGenes(cds)
cds <- estimateSizeFactors(cds)
cds <- estimateDispersions(cds)

#lets look at this again

#cluster first
cds <- clusterCells(cds,verbose = T,num_clusters=10,cores=10)
#remove outliers of group 4 
pData(cds)$cell_coor<-pData(cds)$cell
#change those to HCC1143S so they will not be outlier branches
pData(cds)$cell_coor[which((pData(cds)$cell=="MDA" | pData(cds)$cell=="SUM"  | pData(cds)$cell=="HCC1806" | pData(cds)$cell=="HCC1143G") & pData(cds)$Cluster==9)]<-"HCC1143S"





cds <- suppressWarnings(partitionCells(cds,partition_names ="cell_coor"))



cds <- learnGraph(cds, max_components = 2, RGE_method = 'SimplePPT', verbose = T,partition_group="cell_coor",prune_graph=T)


cds<-orderCells(cds,root_pr_nodes=c("Y_380","Y_54","Y_282","Y_162","Y_499"))
dp_mst <- minSpanningTree(cds)
reduced_dim_coords <- reducedDimK(cds)
ica_space_df <- data.frame(Matrix::t(reduced_dim_coords[1:2,]))
colnames(ica_space_df) <- c("prin_graph_dim_1", "prin_graph_dim_2")
ica_space_df$sample_name <- row.names(ica_space_df)
ica_space_df$sample_state <- row.names(ica_space_df)
edge_list <- as.data.frame(get.edgelist(dp_mst))
colnames(edge_list) <- c("source", "target")

edge_df <- merge(ica_space_df, edge_list, by.x = "sample_name",by.y = "source", all = TRUE)
edge_df <- plyr::rename(edge_df, c(prin_graph_dim_1 = "source_prin_graph_dim_1",prin_graph_dim_2 = "source_prin_graph_dim_2"))
edge_df <- merge(edge_df, ica_space_df[, c("sample_name","prin_graph_dim_1", "prin_graph_dim_2")],by.x = "target", by.y = "sample_name", all = TRUE)
edge_df <- plyr::rename(edge_df, c(prin_graph_dim_1 = "target_prin_graph_dim_1",prin_graph_dim_2 = "target_prin_graph_dim_2"))
write.table(as.matrix(edge_df),file="./monocle3_branchpoints2.txt",col.names=TRUE,row.names=FALSE,sep="\t",quote=FALSE)

p<-plot_cell_trajectory(cds,cell_size=0.1,backbone_color="#000000",color_by = "Cluster",show_state_name=T,alpha=0.3)
ggsave(plot=p,filename="./monocle3.cluster.plot2.png",width=5,height=4,dpi=900)
ggsave(plot=p,filename="./monocle3.cluster.plot2.pdf",width=5,height=4)

p<-plot_cell_trajectory(cds,cell_size=0.1,color_by = "cell",backbone_color="#000000",show_state_name=T,alpha=0.3)
ggsave(plot=p,filename="./monocle3.annot.plot2.png",width=5,height=4,dpi=900)
ggsave(plot=p,filename="./monocle3.annot.plot2.pdf",width=5,height=4)

p<-plot_cell_trajectory(cds,cell_size=0.1,color_by = "treatment",backbone_color="#000000",show_state_name=T,alpha=0.3)
ggsave(plot=p,filename="./monocle3.treat.plot2.png",width=5,height=4,dpi=900)
ggsave(plot=p,filename="./monocle3.treat.plot2.pdf",width=5,height=4)



p<-ggplot(edge_df,aes(x=source_prin_graph_dim_1,y=source_prin_graph_dim_2,xend=target_prin_graph_dim_1,yend=target_prin_graph_dim_2))+geom_segment()+geom_text(color="red",label=edge_df$sample_name,size=2,check_overlap=TRUE)
ggsave(plot=p,filename="./monocle3.branchname.plot2.png",width=5,height=4,dpi=900)
p<-plot_cell_trajectory(cds)
ggsave(plot=p,filename="./monocle3.ptime.plot2.png",width=5,height=4,dpi=900)

saveRDS(cds,file="coembed_monocle3_res.rds")

library(monocle)
library(Seurat)
library(stringr)
#make cds
cds <- readRDS(file="coembed_monocle3_res.rds")


# writing out final data frames
write.table(as.matrix(pData(cds)),file="./monocle3_cells.txt",col.names=TRUE,row.names=TRUE,sep="\t",quote=FALSE)
write.table(as.matrix(Biobase::exprs(cds)),file="./monocle3_aggragated_cells_count.txt",col.names=TRUE,row.names=TRUE,sep="\t",quote=FALSE)
write.table(as.matrix(fData(cds)),file="./monocle3_features.txt",col.names=TRUE,row.names=FALSE,sep="\t",quote=FALSE)


pseudotime<-as.data.frame(pData(cds)$Pseudotime)
row.names(pseudotime)<-row.names(pData(cds))


write.table(as.matrix(pseudotime),file="./RNA_ATAC_pseudotime_final",col.names=F,row.names=T,sep="\t",quote=FALSE)

```


Do the ordering with RNA
```{r}
ibrary(monocle)
library(Seurat)
library(stringr)
#make cds
#Load Seurat object of combedding
seurat_object<-readRDS("scRNA_singlet_filt.rds")

cell<-str_split_fixed(seurat_object[["annot"]][,1],"_",2)[,1]
cell<-gsub("Trametinib","Tram",cell)
cell<-gsub("HCCMDAMB468","MDA",cell)
cell<-gsub("SUM149PT","SUM",cell)
cellt<-str_split_fixed(cell,"_",2)[,1]
treatment<-str_split_fixed(cell,"_",2)[,2]
celltype<-seurat_object[["annot"]]
celltype$cell<-cellt
celltype$treatment<-treatment
celltype$annot<-NULL
seurat_object <- AddMetaData(seurat_object, metadata = celltype)



#Extract data, phenotype data, and feature data from the SeuratObject
data <- as(as.matrix(seurat_object@assays$RNA@data), 'sparseMatrix')

pd <- new('AnnotatedDataFrame', data = seurat_object@meta.data)

fData <- data.frame(gene_short_name = row.names(data), row.names = row.names(data))
fd <- new('AnnotatedDataFrame', data = fData)

#Construct monocle cds
monocle_cds <- newCellDataSet(data,
                              phenoData = pd,
                              featureData = fd,
                              lowerDetectionLimit = 0.5,
                              expressionFamily = negbinomial.size())

FM <- exprs(monocle_cds)
monocle_cds@auxOrderingData$normalize_expr_data <- FM

pca_res<- Embeddings(seurat_object, reduction= "pca")
#PCA
monocle_cds@normalized_data_projection <- as.matrix(t(pca_res))


cds_dims_data<- read.delim("PCA_singlet.proj.UMAP.dims",header=F,row.names=1)



dim_no<-ncol(cds_dims_data)
S <- t(cds_dims_data)
Y <- S
W <- as.matrix(t(pca_res))
#(seurat_object$cca.aligned@cell.embeddings)
A <- S
colnames(A) <- colnames(monocle_cds)
colnames(S) <- colnames(monocle_cds)
colnames(Y) <- colnames(monocle_cds)
reducedDimA(monocle_cds) <- A
monocle_cds@reducedDimW<- W
monocle_cds@reducedDimS <- as.matrix(Y)
monocle_cds@reducedDimK <- S
monocle_cds@dim_reduce_type <- "UMAP"
pData(monocle_cds)$umap_1 = reducedDimA(monocle_cds)[1, ]
pData(monocle_cds)$umap_2 = reducedDimA(monocle_cds)[2, ]
if(dim_no==3){
  pData(monocle_cds)$umap_3 = reducedDimA(monocle_cds)[3, ]
}


saveRDS(monocle_cds,file="Monocle3_justRNA_format.rds")

cds<-monocle_cds

cds <- detectGenes(cds)
cds <- estimateSizeFactors(cds)
cds <- estimateDispersions(cds)

#lets look at this again

#cluster first
cds <- clusterCells(cds,verbose = T,num_clusters=10,cores=10)
#remove outliers of group 4 
pData(cds)$cell_coor<-pData(cds)$cell
#change those to HCC1143S so they will not be outlier branches
pData(cds)$cell_coor[which((pData(cds)$cell=="MDA" | pData(cds)$cell=="SUM"  | pData(cds)$cell=="HCC1806" | pData(cds)$cell=="HCC1143G") & pData(cds)$Cluster==7)]<-"HCC1143S"


cds <- suppressWarnings(partitionCells(cds,partition_names ="cell_coor"))
cds <- learnGraph(cds, max_components = 2, RGE_method = 'SimplePPT', verbose = T,partition_group="cell_coor",prune_graph=T)

#"Y_440","Y_428"
cds<-orderCells(cds,root_pr_nodes=c("Y_440","Y_57","Y_168","Y_542","Y_308"))
dp_mst <- minSpanningTree(cds)
reduced_dim_coords <- reducedDimK(cds)
ica_space_df <- data.frame(Matrix::t(reduced_dim_coords[1:2,]))
colnames(ica_space_df) <- c("prin_graph_dim_1", "prin_graph_dim_2")
ica_space_df$sample_name <- row.names(ica_space_df)
ica_space_df$sample_state <- row.names(ica_space_df)
edge_list <- as.data.frame(get.edgelist(dp_mst))
colnames(edge_list) <- c("source", "target")

edge_df <- merge(ica_space_df, edge_list, by.x = "sample_name",by.y = "source", all = TRUE)
edge_df <- plyr::rename(edge_df, c(prin_graph_dim_1 = "source_prin_graph_dim_1",prin_graph_dim_2 = "source_prin_graph_dim_2"))
edge_df <- merge(edge_df, ica_space_df[, c("sample_name","prin_graph_dim_1", "prin_graph_dim_2")],by.x = "target", by.y = "sample_name", all = TRUE)
edge_df <- plyr::rename(edge_df, c(prin_graph_dim_1 = "target_prin_graph_dim_1",prin_graph_dim_2 = "target_prin_graph_dim_2"))
write.table(as.matrix(edge_df),file="./monocle3_scRNA_branchpoints2.txt",col.names=TRUE,row.names=FALSE,sep="\t",quote=FALSE)

p<-plot_cell_trajectory(cds,cell_size=0.1,backbone_color="#000000",color_by = "Cluster",show_state_name=T,alpha=0.3)
ggsave(plot=p,filename="./monocle3.cluster.plot2.png",width=5,height=4,dpi=900)
ggsave(plot=p,filename="./monocle3.cluster.plot2.pdf",width=5,height=4)

p<-plot_cell_trajectory(cds,cell_size=0.1,color_by = "cell",backbone_color="#000000",show_state_name=T,alpha=0.3)
ggsave(plot=p,filename="./monocle3.annot.plot2.png",width=5,height=4,dpi=900)
ggsave(plot=p,filename="./monocle3.annot.plot2.pdf",width=5,height=4)

p<-plot_cell_trajectory(cds,cell_size=0.1,color_by = "treatment",backbone_color="#000000",show_state_name=T,alpha=0.3)
ggsave(plot=p,filename="./monocle3.treat.plot2.png",width=5,height=4,dpi=900)
ggsave(plot=p,filename="./monocle3.treat.plot2.pdf",width=5,height=4)



p<-ggplot(edge_df,aes(x=source_prin_graph_dim_1,y=source_prin_graph_dim_2,xend=target_prin_graph_dim_1,yend=target_prin_graph_dim_2))+geom_segment()+geom_text(color="red",label=edge_df$sample_name,size=2,check_overlap=TRUE)
ggsave(plot=p,filename="./monocle3.branchname.plot2.png",width=5,height=4,dpi=900)
p<-plot_cell_trajectory(cds)
ggsave(plot=p,filename="./monocle3.ptime.plot2.png",width=5,height=4,dpi=900)

#saveRDS(cds,file="scRNA_ordered_monocle3_res.rds")

library(monocle)
library(Seurat)
library(stringr)
#make cds
#cds <- readRDS(file="coembed_monocle3_res.rds")


# writing out final data frames
#write.table(as.matrix(pData(cds)),file="./monocle3_cells.txt",col.names=TRUE,row.names=TRUE,sep="\t",quote=FALSE)
#write.table(as.matrix(Biobase::exprs(cds)),file="./monocle3_aggragated_cells_count.txt",col.names=TRUE,row.names=TRUE,sep="\t",quote=FALSE)
#write.table(as.matrix(fData(cds)),file="./monocle3_features.txt",col.names=TRUE,row.names=FALSE,sep="\t",quote=FALSE)


pseudotime<-as.data.frame(pData(cds)$Pseudotime)
row.names(pseudotime)<-row.names(pData(cds))


write.table(as.matrix(pseudotime),file="./RNA_pseudotime_final.val",col.names=F,row.names=T,sep="\t",quote=FALSE)

```


Do the ordering with ATAC
```{r}
suppressWarnings(library(monocle))
library(stringr)
message("Loading Monocle3")
# reading in matrix, annotation, and dimension data
cds_cell_data <- read.delim("..//cds_cell_data.txt")
cds_dims_data <- read.table("../cds_dims_data.txt",header=F,row.names=1)
cds_site_data <- read.delim("../cds_site_data.txt")
cds_counts_matrix <- read.table("../cds_counts_matrix.txt")
message("Read in CDS Files.")
rownames(cds_cell_data)==rownames(cds_dims_data)
cds_cell_data<-cbind(cds_cell_data,cds_dims_data)
# generating cell data set
feature_data <- new("AnnotatedDataFrame", data = cds_site_data)
sample_data <- new("AnnotatedDataFrame", data = cds_cell_data)
dimensions_data <- new("AnnotatedDataFrame", data = cds_dims_data)
cds <- suppressWarnings(newCellDataSet(as.matrix(cds_counts_matrix), phenoData = sample_data, featureData = feature_data))
set.seed(2017)
pData(cds)$cells <- NULL
cds@expressionFamily@vfamily<-"binomialff"
cds <- detectGenes(cds)
cds <- estimateSizeFactors(cds)
#cds <- estimateDispersions(cds)
FM <- exprs(cds)
cds@auxOrderingData$normalize_expr_data <- FM
irlba_pca_res<-t(read.table("../180227_180214.U54.merged.bbrd.q10.5k.filt.500.counts.filt_1000_10.fine.tune.cistopic.matrix",header=T,row.names=1))
#irlba_pca_res = irlba_pca_res[match(rownames(irlba_pca_res),colnames(cds)),]
#added in matching, better than match 
matchnum<-rownames(irlba_pca_res) %in% colnames(cds)
irlba_pca_res = irlba_pca_res[matchnum,]
num_dim<-ncol(irlba_pca_res)
cds@normalized_data_projection <- as.matrix(irlba_pca_res)
dim_no<-ncol(cds_dims_data)
S <- t(cds_dims_data)
Y <- S
W <- as.matrix(t(irlba_pca_res))
A <- S
colnames(A) <- colnames(cds)
colnames(S) <- colnames(cds)
colnames(Y) <- colnames(cds)
reducedDimA(cds) <- A
cds@reducedDimW<- W
cds@reducedDimS <- as.matrix(Y)
cds@reducedDimK <- S
cds@dim_reduce_type <- "UMAP"
pData(cds)$umap_1 = reducedDimA(cds)[1, ]
pData(cds)$umap_2 = reducedDimA(cds)[2, ]
if(dim_no==3){
  pData(cds)$umap_3 = reducedDimA(cds)[3, ]
}

pData(cds)$cell<-str_split_fixed(pData(cds)$timepoint, "_", 3)[,1]
cds <- clusterCells(cds,verbose = T,num_clusters=6,cores=10)
pData(cds)$cell_coor<-pData(cds)$cell
#change cells in cluster to HCC1143S so they will not be outlier branches
pData(cds)$cell_coor[which((pData(cds)$cell=="MDA" | pData(cds)$cell=="SUM"  | pData(cds)$cell=="HCC1806" | pData(cds)$cell=="HCC1143G") & pData(cds)$Cluster==2)]<-"HCC1143S"
cds <- suppressWarnings(partitionCells(cds,partition_names ="cell_coor"))
cds <- learnGraph(cds, max_components = 3, RGE_method = 'DDRTree', verbose = T,partition_group="cell_coor",prune_graph=T)
#these were the old atac ones
#start_cells<-c("GAATGAATGCGGTTGGAACATGCGAGGTACTGGTTG","AATACCTGCTGCGGACGTGCGTAAGATGGCTCATAT","AGTCTTAAGCGGTTGGAATGACCATCGACCGTTACT","CGCTCATTCTGCGGACGTTAAGATTATTAACTCATA","ATTACTCGAGGTTGCAAGAGGATAGGTGGCTCATAT")
start_cells=c("TAATGCGCTGCCTCGCAAAGGATAGGCTCAGAATAA","AATACCTGCCGAAGGTTAGCGTAAGACAGCCATGAT","ATTCAGAATGCGTCTATAACGTCCTGTCTGACGAAC","CGCTCATTTGCCTCGCAACTTCGCCTTTAACTCATA","ATTACTCGGCGGTTGGAAGTCAGTACGCATTAGGCG")



#first
#"TAATGCGCTGCCTCGCAAAGGATAGGCTCAGAATAA"
#"GAATGAATAAGAAGTCTAGCTCCAACGTACTGGTTG"
#"GAATGAATCCGAAGGTTAGGATTCTCACCATAATAA"

#"AGTCTTAACCGGCTGAGCGCTCCAACGTACTGGTTG"
#"AGTCTTAATTCCAAGTAATGACCATCTAGTCGGATG"
#"AGTCTTAATGCCTCGCAATGACCATCTTAACTCATA"
#"ATTCAGAATGCGTCTATAACGTCCTGTCTGACGAAC"

#"CGCTCATTTGCCTCGCAACTTCGCCTTTAACTCATA"
#"CGCTCATTGTATCAATATACGTCCTGGACCGTTACT"
#"CGCTCATTTTATTAAGAATCAGAGCCTTAACTCATA"
#"CGCTCATTCCGGCTGAGCTAAGATTACTCAGAATAA"
cds<-orderCells(cds,root_cells=start_cells)
#I both did analyses where i routed based on nodes and start cells. Values are similar
cds<-orderCells(cds,orthogonal_proj_tip=TRUE,root_pr_nodes=c("Y_227","Y_33","Y_87","Y_150","Y_291"))
dp_mst <- minSpanningTree(cds)
reduced_dim_coords <- reducedDimK(cds)
ica_space_df <- data.frame(Matrix::t(reduced_dim_coords[1:2,]))
colnames(ica_space_df) <- c("prin_graph_dim_1", "prin_graph_dim_2")
ica_space_df$sample_name <- row.names(ica_space_df)
ica_space_df$sample_state <- row.names(ica_space_df)
edge_list <- as.data.frame(get.edgelist(dp_mst))
colnames(edge_list) <- c("source", "target")

edge_df <- merge(ica_space_df, edge_list, by.x = "sample_name",by.y = "source", all = TRUE)
edge_df <- plyr::rename(edge_df, c(prin_graph_dim_1 = "source_prin_graph_dim_1",prin_graph_dim_2 = "source_prin_graph_dim_2"))
edge_df <- merge(edge_df, ica_space_df[, c("sample_name","prin_graph_dim_1", "prin_graph_dim_2")],by.x = "target", by.y = "sample_name", all = TRUE)
edge_df <- plyr::rename(edge_df, c(prin_graph_dim_1 = "target_prin_graph_dim_1",prin_graph_dim_2 = "target_prin_graph_dim_2"))
write.table(as.matrix(edge_df),file="./monocle3_branchpoints2.txt",col.names=TRUE,row.names=FALSE,sep="\t",quote=FALSE)

p<-plot_cell_trajectory(cds,cell_size=0.1,color_by = "Cluster",backbone_color="#000000",show_state_name=T,alpha=0.3)
ggsave(plot=p,filename="./monocle3.cluster.plot2.png",width=5,height=4,dpi=900)
ggsave(plot=p,filename="./monocle3.cluster.plot2.pdf",width=5,height=4)

p<-plot_cell_trajectory(cds,cell_size=0.1,color_by = paste(colnames(pData(cds))[1]),backbone_color="#000000",show_state_name=T,alpha=0.3)
ggsave(plot=p,filename="./monocle3.annot.plot2.png",width=5,height=4,dpi=900)
ggsave(plot=p,filename="./monocle3.annot.plot2.pdf",width=5,height=4)

p<-ggplot(edge_df,aes(x=source_prin_graph_dim_1,y=source_prin_graph_dim_2,xend=target_prin_graph_dim_1,yend=target_prin_graph_dim_2))+geom_segment()+geom_text(color="red",label=edge_df$sample_name,size=2,check_overlap=TRUE)
ggsave(plot=p,filename="./monocle3.branchname.plot2.png",width=5,height=4,dpi=900)
p<-plot_cell_trajectory(cds)
ggsave(plot=p,filename="./monocle3.ptime.plot2.png",width=5,height=4,dpi=900)

# writing out final data frames
#write.table(as.matrix(pData(cds)),file="./monocle3_cells.txt",col.names=TRUE,row.names=TRUE,sep="\t",quote=FALSE)
#write.table(as.matrix(Biobase::exprs(cds)),file="./monocle3_aggragated_cells_count.txt",col.names=TRUE,row.names=TRUE,sep="\t",quote=FALSE)
#write.table(as.matrix(fData(cds)),file="./monocle3_features.txt",col.names=TRUE,row.names=FALSE,sep="\t",quote=FALSE)
pseudotime<-as.data.frame(pData(cds)$Pseudotime)
row.names(pseudotime)<-row.names(pData(cds))
write.table(as.matrix(pseudotime),file="./ATAC_pseudotime_final.val",col.names=F,row.names=T,sep="\t",quote=FALSE)
#this is what worked
saveRDS(cds,"./save.final_double_check.cds")
```





#comparison analysis
```{r}

library(ggplot2)
library(stringr)
library(ggpubr)
#ordering where cells are chosen
#ATAC<-read.delim(file="ATAC.val",header = F)
#ordering where branches are chosen
ATAC<-read.delim(file="ATAC_pseudotime_final.val",header = F)
RNA<-read.delim(file="RNA_pseudotime_final.val",header = F)
ATAC_RNA<-read.delim(file="./RNA_ATAC_pseudotime_final.val",header = F)
annot<-read.delim(file="180227_180214.U54.merged_new.annot",header = F)
RNA_annot<-read.delim(file="RNA_orig.annot",header = F)
cells<-str_split_fixed(annot$V2, "_", 3)[,1]
comparison=data.frame(ATAC=ATAC$V2,Combined=ATAC_RNA$V2[match(ATAC$V1,ATAC_RNA$V1)],annot=annot$V2[match(ATAC$V1,annot$V1)],cell=cells[match(ATAC$V1,annot$V1)])
row.names(comparison)<-ATAC$V1
order(ATAC$V2)

plot_list=list()
for (i in levels(comparison$cell))
{
temp<-comparison[which(comparison$cell==paste0(i)),]
ordered<-order(temp$ATAC)
final<-cbind(temp[ordered,],ATAC_ordered=1:dim(temp)[1])
ordered<-order(final$Combined)
final<-cbind(final[ordered,],Combined_ordered=1:dim(final)[1])
#print(row.names(final[final$Combined==min(final$Combined),]))
print(paste0(i))
print(cor(final$ATAC,final$Combined,method="spearman"))
p<-ggplot(final,aes(x=Combined,y=ATAC,color=annot))+geom_point()+theme_classic()+scale_colour_manual(values = c("HCC1143G_DMSO" = "#99000d","HCC1143G_Tram" = "#fcbba1","HCC1143S_DMSO" = "#e66101","HCC1143S_Tram" = "#fdb863","HCC1806_DMSO" = "#006d2c","HCC1806_Tram" = "#74c476","MDA_DMSO" = "#045a8d","MDA_Tram" = "#a6bddb","SUM_DMSO" = "#810f7c","SUM_Tram" = "#8c6bb1"))
plot_list[[paste0(i)]]<-p 
}

res<-ggarrange(plotlist=plot_list,ncol=2,nrow=3)
ggsave(res,filename = "Matchup.ATAC.pdf")

ggsave(plot_list[["SUM"]]+theme(legend.position="none"),filename = "Matchup.atac.SUM.pdf",width = 5.5,height = 5.5,units = "cm")

#same RNA
annot<-RNA_annot
cells<-str_split_fixed(annot$V2, "_", 3)[,1]
ATAC<-RNA
comparison=data.frame(ATAC=ATAC$V2,Combined=ATAC_RNA$V2[match(ATAC$V1,ATAC_RNA$V1)],annot=annot$V2[match(ATAC$V1,annot$V1)],cell=cells[match(ATAC$V1,annot$V1)])
row.names(comparison)<-ATAC$V1
order(ATAC$V2)
plot_list=list()
for (i in levels(comparison$cell))
{
  temp<-comparison[which(comparison$cell==paste0(i)),]
  ordered<-order(temp$ATAC)
  final<-cbind(temp[ordered,],ATAC_ordered=1:dim(temp)[1])
  ordered<-order(final$Combined)
  final<-cbind(final[ordered,],Combined_ordered=1:dim(final)[1])
  #print(row.names(final[final$Combined==min(final$Combined),]))
  print(paste0(i))
  print(cor(final$ATAC,final$Combined,method="spearman"))
  p<-ggplot(final,aes(x=Combined,y=ATAC,color=annot))+geom_point()+ylab("RNA")+theme_classic()+scale_colour_manual(values = c("HCC1143G_DMSO" = "#8c510a","HCC1143G_Trametinib" = "#bf812d","HCC1143S_DMSO" = "#dfc27d","HCC1143S_Trametinib" = "#f6e8c3","HCC1806_DMSO" = "#4d9221","HCC1806_Trametinib" = "#c7e9b4","HCCMDAMB468_DMSO" = "#35978f","HCCMDAMB468_Trametinib" = "#41b6c4","SUM149PT_DMSO" = "#c51b7d","SUM149PT_Trametinib" = "#de77ae"))
  plot_list[[paste0(i)]]<-p +theme(legend.position="none")
}

res<-ggarrange(plotlist=plot_list,ncol=2,nrow=3)
ggsave(res,filename = "Matchup.RNA.pdf")

ggsave(plot_list[["SUM149PT"]],filename = "Matchup.rna.SUM.pdf",width = 5.5,height = 5.5,units = "cm")

```



Add a new chunk by clicking the *Insert Chunk* button on the toolbar or by pressing *Ctrl+Alt+I*.

When you save the notebook, an HTML file containing the code and output will be saved alongside it (click the *Preview* button or press *Ctrl+Shift+K* to preview the HTML file).

The preview shows you a rendered HTML copy of the contents of the editor. Consequently, unlike *Knit*, *Preview* does not run any R code chunks. Instead, the output of the chunk when it was last run in the editor is displayed.
